---
title: "ISO/OGC Standards coverage in geometa"
author: Emmanuel Blondel
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE
)
#compute coverage
require(geometa, quietly = TRUE)
cov <- geometa_coverage()

#coverage summary
stds <- unique(cov$specification)
stds <- stds[order(stds)]
cov_summary <- do.call("rbind", lapply(stds, function(std){
  cov_std <- cov[cov$specification == std,]
  cov_std_per <- round(nrow(cov_std[cov_std$in_geometa,]) / nrow(cov_std) * 100,2)
  cov_std_in <- nrow(cov_std[cov_std$in_geometa,])
  cov_std_out <- nrow(cov_std[!cov_std$in_geometa,])
  cov_out <- data.frame(
    Standard = std,
    Title = cov_std$title[1],
    Namespace = cov_std$ns_prefix[1],
    Supported = cov_std_in,
    Missing = cov_std_out,
    Coverage = cov_std_per,
    stringsAsFactors = FALSE
  )
  return(cov_out)
}))
cov_summary$coverage_class <- floor(cov_summary$Coverage/20)
row.names(cov_summary) <- cov_summary$Standard

cov_summary <- rbind(
  cov_summary[startsWith(cov_summary$Standard, "ISO"),],
  cov_summary[startsWith(cov_summary$Standard, "GML"),]
)

#cov_summary_md (for README)
cov_summary_md <- cov_summary
cov_summary_md$Coverage <- sapply(1:nrow(cov_summary_md), function(i){
  cov <- cov_summary_md[i,]
  sprintf("[![%1$s](%2$s)](%3$s)",
      row.names(cov),
      URLencode(gsub("PERCENT","%",sprintf("https://img.shields.io/badge/%1$s-%2$sPERCENT-%3$s.svg",
        "",round(cov$Coverage),
        switch(as.character(cov$coverage_class),
           "0" = "ad0f0f",
           "1" = "ff0c0c",
           "2" = "f9ae2c",
           "3" = "f2eb24",
           "4" = "33cc7a",
           "5" = "4a4ea8"
        )))
      ),
      "https://github.com/eblondel/geometa"
  )
})
cov_summary_md$coverage_class <- NULL
cov_summary_md$Standard <- row.names(cov_summary_md) 
cov_summary_md <- cov_summary_md[,c("Standard","Title","Namespace","Coverage","Supported","Missing")]
row.names(cov_summary_md) <- NULL
kable(cov_summary_md, format = "markdown")



```

As measure of quality assurance, and due to the large number of classes available in the ISO/OGC standards, a set of functions was provided to assess how much ISO/OGC standards are covered by ``geometa`` classes. The present document has been generated to report on the percentage of completeness of these standards, and provide the detailed list of ISO/OGC standards classes and its status in ``geometa``.

Some specific classes may be still missing, and will be added iteratively, according to the needs, status highlighted for the different standards. This applies particularly to GML classes (ISO 19136) that may be needed in some ISO 19115 and 19110 classes. In case of a missing class, [create a ticket](https://github.com/eblondel/geometa/issues/new).

## ISO/OGC Metadata standards coverage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(cov_summary_md,format = "markdown")

```


## ISO/OGC Metadata classes inventory

TODO